---
title: "Beer Study Notebook"
output:
  html_document:
    df_print: paged
---


```{r}
# Beer Study
library(dlookr)
library(visdat)
library(plotly)
library(missRanger)
library(ggplot2)
library(magrittr)
library(ranger)
library(dplyr)
library(class)
library(caret)
library(e1071)
library(GGally)
library(stringi)
library(stringr)
library(xgboost)
library(car)
library(Matrix)
library(keras)
library(forecast)
library(neuralnet)
```
# This is to add in all of the librarys we are using for the code.
```{r}
Beers = read.csv('/Users/ZacharyHarris/Desktop/MS Data Science/MSDS_6306_Doing-Data-Science-Master/Unit 8 and 9 Case Study 1/Beers.csv')
Breweries = read.csv('/Users/ZacharyHarris/Desktop/MS Data Science/MSDS_6306_Doing-Data-Science-Master/Unit 8 and 9 Case Study 1/Breweries.csv')
Breweries = Breweries %>% filter(!is.na(Name))
Beers2 = Beers
JoinedData_Unclean = left_join(Beers2,Breweries,bu = c("Brewery_id" = "Brew_ID"))
Beers2$IBU = imputate_na(Beers,IBU,ABV, method = "mice") # Filling in Missing IBU
Beers2$ABV = imputate_na(Beers,ABV,IBU, method = "mice") # Filling in Missing ABV
JoinedData = left_join(Beers2,Breweries,by = c("Brewery_id" = "Brew_ID"))
```
# This is to load, join, and fill in missing data from both the breweries and the beers data set.We had used the imputate.na() function to fill in the missing data with projections as opposed to random numbers.

```{r}
head(JoinedData, 6)
tail(JoinedData, 6)

#plot_na_pareto(JoinedData, only_na = TRUE)
#plot_na_intersect(JoinedData)
#vis_miss(JoinedData)
```
# We are now looking to make sure that we didn't miss any of the data points and we have a solid block of data.

```{r}
Medians = JoinedData %>% group_by(State) %>% summarize(median_ABV = median(ABV),median_IBU = median(IBU)) #Defining Medians

Medians %>% ggplot(aes(x = median_ABV, fill = State)) + geom_histogram() #Plotting Medians


JoinedData[which.max(JoinedData$IBU),] %>% select(State) #Max IBU by state
JoinedData[which.max(JoinedData$ABV),] %>% select(State) #Max ABV by state
```
# Now we are looking at the Joined Data to determine which state has the highest IBU and ABV.
```{r}
summary(JoinedData) # Summary of Data


JoinedData %>% ggplot(aes(x = ABV, y = IBU, color = State)) + geom_jitter() + geom_smooth() # Scatterplot
JoinedData %>% select(ABV,IBU) %>% ggpairs() # Deriving Correlation


